\Sof{TBA - New Titles in the comments}

### 2020-05-08 paper/icsme20.tex
motivation

As an example, consider the patch of the TLS state-machine protocol implementation in 
OpenSSL\footnoteref{openssl} to address a memory leak flaw found in the way OpenSSL 
handled TLS status request extension data during session renegotiation.multiple memory leaks 
where a remote attacker could cause a Denial-of-Service
(DoS) attack - through memory consumption - via large OCSP Status Request extensions.
The Online Certificate Status Protocol (OCSP) is a protocol that allows the client to 
verify the server certificate for revocation without messing with certificate revocation 
lists. This extension however, enables a TLS server to include its response in the handshake.

@@

Every SSL/TLS connection begins with a handshake 
which is responsible by the negotiation between the two parties. 
The OSCP Status Request extension allows the client to verify
the server certificate. The problem in CVE-$2016$-$6304$
is that if the client sistematically requests a renegotiation,
while sending large OCSP Status Request extensions each time,
then there will be unbounded memory growth on the server
and lead to a Denial-of-Service attack through memory exhaustion.

>>>>

As an example, consider the patch of the Online Certificate Status Procotol (OCSP) 
implementation in OpenSSL\footnoteref{openssl} to address a memory leak flaw 
found in the way OpenSSL handled TLS status request extension data during session 
renegotiation and where a remote attacker could cause a Denial-of-Service
(DoS) attack - through memory consumption - via large OCSP Status Request extensions.
OCSP, formally known as the TLS Certificate Status Request extension, is a protocol 
that allows the client to verify the server certificate for revocation.

@@

Every SSL/TLS connection begins with a handshake 
which is responsible for the negotiation between the two parties. 
The OSCP Status Request extension allows the client to verify
the server certificate and enables a TLS server to include
its response in the handshake. The problem in CVE-$2016$-$6304$
is that if the client systematically requests a renegotiation,
while sending large OCSP Status Request extensions each time,
then there will be unbounded memory growth on the server
and lead to a Denial-of-Service attack through memory exhaustion. 
Applications not enabling OCSP stapling support are not affected.
